---
title: "rscrape"
author: "Tyler Miguel"
date: "11/17/2016"
output:
  html_document
---

# Scraping data from website in R

## Introduction

The content below we be a step-by-step introduction guide as to how to scrape data from websites, using R. We will focus on scraping movie data in R, and then move up to more involved projects.

This is the first in the series.

## Downloading packages

First, we need to download the packages we are going to use. You can see below that I just called the packages using the library function, but if you don't already have the libraries installed, in stall them by using 'install.packages()'. 

```{r, message=FALSE}

library(rvest)
library(dplyr)
library(XML)

```

## Decide which URL you would like to scrape

Now that the packages are loaded into the environment, we are going to take a look at an easy example of scraping data from an imdb webite.

We are interested in scraping text data from a text table on the Deadpool imdb website. (great movie) 

To do this, we must first locate the URL to the website, and then assign this URL to a variable called "movie". The 'read_html' function takes a URL and converts it into a connection. We assign this connection to the variable "movie".


```{r}
movie <- read_html("http://www.imdb.com/title/tt1431045/")
```

## Parse text data from website

Now that we have a connection variable called "movie", we will use this variable and pass it through functions to extract the data we are looking for.

We will use 'html_node' to extract pieces of the html data that we can access. Using a CSS selector (we used selector gadget, a google chrome extention) we are able to highlight which part of the website we would like to pull the data from. Selector gadget will then tell you the title of the section of data you want to select. You can pass this title through the 'html_node' and use 'html_text' to extract the text from html. We will assign this data to a new variable called summarydata.

Additionally, we used the pipe operator from the dplyr package, so if you are not farmilar with this, and the code below looks confusing to you, feel free to read about it and come back to this chunk of code. 

```{r}
summarydata <- movie %>% html_node(".summary_text") %>% html_text() 
## .summary_text is from CSS selector
```

## Print data

Now that we have 'summarydata' as a new variable, we will go ahead and print it to our console.

```{r}
summarydata
```

As you can see, we were able to extract the line of text right below the trailer video (go onto the website to see what I'm talking about).
